Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-07 draft.tex
explain which state variables are possible for investment; rewrite defn of SQ eqm

\vskip.5in
We have six state variables, so $s = \left(q_s,q_g,l_s,l_g,w_s,w_g \right)$.
\begin{itemize}
	\item Strategies for the patron and $c$ are also how much to invest in each of the six state variables. Some can be ruled out by preference assumptions:
		\begin{itemize}
			\item $c$ dislikes war, so will never invest in $w_s$ or $w_g$. It would also not want to make the government lose, so won't invest in $l_g$ either.
			\item Because the patron's preferences are aligned with the secessionists and against the government, it never invests in $w_g$ or $l_s$.
		\end{itemize}
	\item This leaves four state varibles in which the patron may invest: $q_s$, $q_g$, $l_g$ and $w_s$. Three in which $c$ may invest: $q_s$, $q_g$, $l_s$.
\end{itemize}

\vskip1in
\begin{definition}
 The Status Quo Equilibrium is a stationary Markov equilibrium in which the outcome is perpetual unrecognized statehood.

On the equilibrium path, the patron invests to avoid the reunification outcome. That is, it invests in the secessionists' status quo payoffs to deter the international community from investing in the secessionists' payoffs from ceding. In period $t$, the patron invests $R_{pt} = \max\left\{\frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right),0\right\}$ to augment the status quo payoffs of the secessionists, $q_{st}$. Player $c$ then chooses $R_{ct} =0$ so that playing status quo is a best response for both inside players. (SQ,SQ) is played in the third stage and the game continues to period $t+1$.

If instead $R_{pt} < \frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right)$ (i.e. assumption 3 doesn't hold), player $c$ will invest $R_{ct} = l_{st} - \left(q_{st} + R_{pt} \right) + \ve$, for $\ve$ small, to augment $l_{st}$. In this case, status quo remains a best response for the government but cede becomes the best response for the secessionists. The game ends with the secessionist territory being reunited. This path is ruled out by Assumption 3 (see Lemma 2).

The patron would prefer to invest to provoke the recognition outcome, which it can attempt to do directly by investing in the government's payoffs from ceding, $l_{gt}$. If the patron invests $R_{pt} > \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_{gt}$, player $c$ will then choose $R_{ct} = 0$ and cede will be the best response for the government. Status quo remains the best response for the secessionists, so the game ends with the secessionists gaining recognition. This path is ruled out by Assumption 4 (see Lemma 3).

As long as $R_{pt} \leq \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$, player $c$ will counter with $R_{ct} = R_{pt} - \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_{gt}$. This makes status quo a best response for the government as well as for the secessionists so that the status quo equilibrium is played and the game continues to period $t+1$. Note that the optimal investments in the government's payoffs zero.

Instead of instigating recognition directly by improving the government's payoffs from ceding, the patron might want to instigate fighting, which would lead to recognition with probability $p_{1s}$. If the patron invests $R_{pt}p_{1s} > \frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$ to augment $w_{s,t}$, player $c$ will choose $R_{ct}=0$ and Fight becomes a best response for the secessionists so (SQ,Fight) is played in third stage. The game will end with an outcome that depends on the war lottery. This path is ruled out by a combination of Assumptions 3 and 4 (see Lemma 4).

If the patron spends less than this amount, player $c$ will counter by investing $R_{ct} = R_{pt}p_{1s} + \mu - Q_{s,t-1} + \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$ in $q_{st}$, the secessionists' status quo payoffs. This makes playing Status Quo a best response for both players so that the status quo equilibrium is played and the game continues to period $t+1$. Here again the optimal investment by both parties is zero.\footnote{Note that the patron could also invest in $q_{gt}$ to counter investment by player $c$ in the government's payoffs from war. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.}
\end{definition}

>>>>

The state is a vector of six variables comprised of the payoffs from the status quo, ceding, and winning the issue of status for each of the two inside actors. That is, $s = \left(q_s,q_g,l_s,l_g,w_s,w_g \right)$. Strategies for the patron and the international community are how much to invest in each of the six state variables. However, positive investments in some of the state variables can be ruled out by preference assumptions.

Player $c$ dislikes war and so will never invest in $w_s$ or $w_g$, which only serve to increase the likelihood that one of the inside actors chooses to fight. It would also not want to make the government lose and so won't invest in $l_g$. This leaves three state variables in which player $c$ might invest: $q_s$, $q_g$, $l_s$.

Because the patron's preferences are aligned with the secessionists and against the government, it never invests in $w_g$ or $l_s$. The only reason the patron would invest in $q_g$ is to counter an investment by player $c$ in the government's payoffs from war; since player $c$ will not make such an investment, we can also rule out investments by the patron in $q_g$. This leaves four state variables in which the patron may invest: $q_s$, $l_g$ and $w_s$.

In equilibrium, the outside actors' investments are paired: the patron investments in the secessionists' status quo payoffs deter player $c$'s investments in the secessionists' payoffs from ceding. Likewise, investments by player $c$ in the government's status quo payoffs deter the patron from investing in the government's payoffs from ceding. Investments by player $c$ in the secessionists' status quo payoffs deter the patron from investing in the secessionists' payoffs from winning the conflict via fighting. In each case, the investments are sufficient to make the largest continuation payoffs in the game between the secessionists and the government those from playing status quo.

\begin{definition}
The Status Quo Equilibrium is a stationary Markov equilibrium in which the outcome is perpetual unrecognized statehood. The strategy profiles are the following, organized according to the patron's investments in each state variable. In period $t$:

\begin{enumerate}
	\item The patron invests $R_{pt} = \max\left\{\frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right),0\right\}$ to augment $q_{st}$. Player $c$ invests $R_{ct} =0$ in $l_{st}$.

If $R_{pt} < \frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right)$ player $c$ invests $R_{ct} = l_{st} - \left(q_{st} + R_{pt} \right) + \ve$, for $\ve$ small, in $l_{st}$. Cede becomes the unique best response for the secessionists.

	\item As long as $R_{pt} \leq \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_{gt}$, player $c$ invests $R_{ct} = R_{pt} - \left( Q_{g,t-1} - L_{g,t-1}\right)$ in $q_{gt}$. Note that the outcome is that investments in $l_{gt}$ and $q_{gt}$ are zero.

If $R_{pt} > \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_{gt}$, player $c$ invests $R_{ct} = 0$. Cede becomes the unique best response for the government.

	\item As long as $R_{pt} \leq \frac{1}{p_{1s}} \left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right]$ to augment $w_{s,t}$, player $c$ invests $R_{ct} = R_{pt}p_{1s} + \mu - Q_{s,t-1} + \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$ in $q_{st}$. Similar to case two, the outcome is that investments in $w_{st}$ and $q_{st}$ are zero.

If $R_{pt} > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right] $ to augment $w_{s,t}$, player $c$ will choose $R_{ct}=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
The government and secessionists play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted above, playing Status Quo is the best response for both inside actors.
\end{definition}

\textbf{Need text to give intuition or tell where I'm going to give intuition.}
